Ages of Planets and Stars Observed by Kepler

### 2024-04-15 paper/ms.tex
update ms
refactor stellar parameter plotter
(for generality!)

>>>>

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{camd_M_G_vs_dr3_bp_rp.pdf}
		}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{camd_M_G_vs_adopted_Teff.pdf}
		}

		\subfloat{
		\includegraphics[width=0.5\textwidth]{st_params_adopted_logg_vs_adopted_Teff.pdf}
		}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{st_params_dr3_phot_g_mean_mag_vs_adopted_Teff.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf CAMD}.
    (todo)
	}
	\label{fig:camd}
\end{figure*}
